Early Observations of the Type Ia Supernova \abc:\\ Evidence for Strong Ejecta Mixing and/or Interaction with Diffuse Material

### 2017-08-17 doc/ms.tex
Minor grammatical clean up for companion section

\begin{figure}[!thb]
  \centering
  \includegraphics[width=0.48\textwidth]{companion_lc.pdf}
  \caption{Comparison of SN ejecta-companion interaction models 
  with early observations of \abc. $g_\mathrm{PTF}$ observations 
  (green) detections and 3$\sigma$ upper limits are shown 
  as circles and downward arrows, respectively. 
  \textit{Swift}/$UVW1$ observations (magenta) are shown as hexagons.
  The dashed, solid, and dash-dot lines show the expected flux 
  for companion interaction models in the $g_\mathrm{PTF}$ (green) 
  and $UVW1$ (magenta) filters. The models have been adjusted to 
  account for the distance and reddening towards \abc. Each 
  model features a different companion semi-major axis, $a$, and 
  time of explosion, $t_\mathrm{exp}$, as labeled in the 
  legend. While models with $a \gtrsim 10^{12} \, \mathrm{cm}$ can 
  explain the early rise in $g_\mathrm{PTF}$, they greatly 
  overpredict the flux in the UV. Models with $a \approx 10^{11} \, 
  \mathrm{cm}$ can explain the initial detection \abc, but they 
  fail to replicate the $\sim$2 mag rise in the $\sim$24 hr after 
  explosion.
  }
  \label{fig:SN-companion}
\end{figure}

@@

Figure~\ref{fig:SN-companion} additionally shows that a companion at $a \approx 18 \times 10^{11} \, \mathrm{cm}$ provides a good match to the initial $g_\mathrm{PTF}$ rise, if $t_\mathrm{exp} \approx t_0 + 0.1 \; \mathrm{d}$. Models with $a \gtrsim 10^{12} \, \mathrm{cm}$, which can explain the initial $g_\mathrm{PTF}$ rise, signiticantly overpredict the observed UV flux, however. There is no choice of $a$ capable of replicating the early rise of \abc\ without also significantly overpredicting the observed UV flux.

>>>>

@@

\begin{figure}[!thb]
  \centering
  \includegraphics[width=0.48\textwidth]{companion_lc.pdf}
  \caption{Comparison of SN ejecta-companion interaction models 
  with early observations of \abc. $g_\mathrm{PTF}$ 
  detections and 3$\sigma$ upper limits are shown 
  as green circles and downward arrows, respectively. 
  \textit{Swift}/$UVW1$ observations are shown as magenta hexagons.
  The dashed, solid, and dash-dot lines show the expected flux 
  for companion-interaction models in the $g_\mathrm{PTF}$ (green) 
  and $UVW1$ (magenta) filters. The models have been adjusted to 
  account for the distance and reddening towards \abc. Each 
  model features a different companion semi-major axis, $a$, and 
  time of explosion, $t_\mathrm{exp}$, as labeled in the 
  legend. While models with $a \gtrsim 10^{12} \, \mathrm{cm}$ can 
  explain the early optical rise, they greatly 
  overpredict the UV flux. Models with $a \approx 10^{11} \, 
  \mathrm{cm}$ can explain the initial detection \abc, but they 
  fail to replicate the $\sim$2 mag rise in the $\sim$24 hr after 
  explosion.
  }
  \label{fig:SN-companion}
\end{figure}

Figure~\ref{fig:SN-companion} additionally shows that a companion at $a \approx 18 \times 10^{11} \, \mathrm{cm}$ provides a good match to the initial optical rise, if $t_\mathrm{exp} \approx t_0 + 0.1 \; \mathrm{d}$. Models with $a \gtrsim 10^{12} \, \mathrm{cm}$, which can explain the initial $g_\mathrm{PTF}$ rise, signiticantly overpredict the observed UV flux, however. There is no choice of $a$ capable of replicating the early rise of \abc\ without also overpredicting the observed UV flux.
